---
title: "Final"
author: "Arshia Sharma, Betsy Heredia, Kayla Cho, Nawal Alasmari"
subtitle: MGSC 310, Fall 2020, Zoom Professor Hersh
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
library(knitr)
library(forcats)
library(sjPlot)
# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
# knitr::opts_knit$set(root.dir = 'C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')
# setwd('C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')

# set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')


```


```{r}
# if you get an error on loading libraries install package first
# 
library(ISLR)

library("tidyverse")
library('rsample')
library("lubridate")
library("groupdata2")

options(scipen = 50)
set.seed(1818)
hotels <- read.csv(here::here("datasets", "hotel_bookings.csv"))

hotels <- hotels %>% mutate(hotel = as.factor(hotel), is_canceled = as.factor(is_canceled),
                            arrival_date_month = as.factor(arrival_date_month),
                            meal = as.factor(meal),
                            country = as.factor(country), market_segment = as.factor(market_segment), 
                            agent = as.factor(agent), country = as.factor(country),
                            company = as.factor(company),
                            distribution_channel = as.factor(distribution_channel),
                            is_repeated_guest = as.factor(is_repeated_guest),
                            reserved_room_type = as.factor(reserved_room_type), 
                            assigned_room_type = as.factor(assigned_room_type),
                            deposit_type = as.factor(deposit_type), 
                            customer_type = as.factor(customer_type),
                            reservation_status = as.factor(reservation_status),
                            reservation_status_date = mdy(reservation_status_date)) %>% select(-agent, -company, -reservation_status, -country, , -reservation_status_date)

hotels <- hotels %>% filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(market_segment),
             !is.na(adr))

#splitting the data 80%-20%
train_pop <- 0.80
hotels_split <- initial_split(hotels, prop = train_pop)

hotels_train <- hotels_split %>% training()
hotels_test <- hotels_split %>% testing()

hotels_train <-upsample(hotels_train, cat_col = "is_canceled")

hotels_test <- subset(hotels_test, distribution_channel != "Undefined")
```

## 1. Looking over the database
```{r}
summary(hotels)

glimpse(hotels)

nlevels(hotels$agent)

```

## Data Visualizations 

Cancellations Based on Assigned Room Type
```{r}
ggplot(hotels ,aes(x=factor(assigned_room_type),fill=factor(is_canceled)))+

geom_bar()+
ggtitle("Cancellations Based on Assigned Room Type")+
  xlab("Assigned Room Type") +
  ylab("Number of Bookings")+
scale_fill_discrete(
    name = "Canceled",
    breaks = c("0", "1"),
    label = c("No", "Yes"))+
  theme(axis.text.x = element_text( size=12),axis.text.y = element_text(size=12))+
  theme_minimal()
```


Cancellations Based on Reserved Room Types
```{r}
ggplot(hotels ,aes(x=factor(reserved_room_type),fill=factor(is_canceled)))+

geom_bar()+
ggtitle("Cancellations Based on Reserved Room Types")+
  xlab("Reserved Room Type") +
  ylab("Number of Bookings")+
scale_fill_discrete(
    name = "Canceled",
    breaks = c("0", "1"),
    label = c("No", "Yes"))+
  theme(axis.text.x = element_text( size=12),axis.text.y = element_text(size=12))+ theme_minimal()
```

Cancellations Based on Hotel Type & Lead Time
```{r}

ggplot(hotels, aes(x=hotel,y=lead_time,fill=factor(is_canceled)))+
  geom_boxplot(position="dodge")+
    xlab(" Hotel Type ")+
    ylab("Lead Time")+
  ggtitle("Cancellations Based on Hotel Type & Lead Time")+
scale_fill_discrete(
    name = "Canceled",
    breaks = c("0", "1"),
    label = c("No", "Yes"))+
  theme(axis.text.x = element_text( size=12),axis.text.y = element_text(size=12))+ theme_minimal()
```


Booking Status by Month
```{r}
ggplot(hotels, aes(arrival_date_month, fill = factor(is_canceled))) +

geom_bar() +
  
coord_flip() + scale_fill_discrete(
    name = "Canceled",
    breaks = c("0", "1"),
    label = c("No", "Yes")) +

labs(title = "Booking Status by Month",
       x = "Month",
       y = "Count") + 

theme(axis.text.x = element_text( size=12),axis.text.y = element_text(size=12))+
  theme_minimal()

```

## 2. Logestic Regression

```{r}

library('forcats')

hotels_mod1 <- glm(is_canceled ~ .,
                     family = binomial,
                     data = hotels_train)

summary(hotels_mod1)


"This code is written using the variable canceled variable - which is a column we have added to the dataframe that represents a binary number (1 or 0) that represents if the guest checked out (1) or cancelled/did not show (0). "
```

```{r}
exp(hotels_mod1$coefficients)

```

Predictions
```{r}

scores_train <- predict(hotels_mod1, 
                       type = "response")

scores_test <- predict(hotels_mod1, 
                       newdata = hotels_test %>% filter(complete.cases(is_canceled)),
                       type = "response")

head(scores_train)
head(scores_test)
```

Residuals & Predictions
```{r}
library('yardstick')

results_train <- data.frame(

  `truth` = hotels_train   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(is_canceled)),
   `Class1` =  scores_train,
   `type` = rep("train",length(scores_train)),
   `predicted` =  as.numeric(ifelse(scores_train> 0.4,1,0)))


results_test <- data.frame(
  `truth` = hotels_test   %>% 
       filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(is_canceled)),
   `Class1` =  scores_test,
   `type` = rep("test",length(scores_test)),
   `predicted` = as.numeric(ifelse(scores_test> 0.4,1,0))) 


head(results_train)
head(results_test)
```

Residuals & Predictions as factors
```{r}
#used for the correlation factors - have to change from numerical to factors

results_train_cm <- data.frame(

  `truth` = hotels_train   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.factor(is_canceled)),
   `Class1` =  scores_train,
   `type` = rep("train",length(scores_train)),
   `predicted` =  as.factor(ifelse(scores_train> 0.4,1,0)))


results_test_cm <- data.frame(
  `truth` = hotels_test   %>% 
       filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.factor(is_canceled)),
   `Class1` =  scores_test,
   `type` = rep("test",length(scores_test)),
   `predicted` = as.factor(ifelse(scores_test> 0.4,1,0))) 
```


```{r}
library('ggplot2')
library('plotROC')
library('yardstick')

ROC_train <- ggplot(results_train, 
            aes(m = Class1, d = is_canceled)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16) + ggtitle("Logistic Model of Train Dataset")
print(ROC_train)

ROC_test <- ggplot(results_test, 
            aes(m = Class1, d = is_canceled)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)+ ggtitle("Logistic Model of Test Dataset")
print(ROC_test)
```

AUC Scores
```{r}

AUC_train <- calc_auc(ROC_train)
print(AUC_train)


AUC_test <- calc_auc(ROC_test)
print(AUC_test) 

```
Confusion Matrix
```{r}

cm_train <- conf_mat(results_train_cm, 
               truth = is_canceled,
               estimate = predicted)

cm_test <- conf_mat(results_test_cm, 
               truth = is_canceled,
               estimate = predicted)

print(cm_train)
print(cm_test)

```

R2, RMSE and Mean Absolute Error predictions.
```{r}

library(yardstick)
calc_train <-  data.frame(
  `truth` = results_train$is_canceled,
  `predicted` = results_train$predicted
)

calc_test <-  data.frame(
  `truth` = results_test$is_canceled,
  `predicted` = results_test$predicted
)

print(metrics(calc_train,truth, predicted))
print(metrics(calc_test,truth, predicted))

```
```{r}
summary(cm_train)
summary(cm_test)
```
## 3.Predict Cancellations using Elastic Net

```{r}
library('tidyverse')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('forcats')
library('broom')
```
1. Elastic Net testing different alphas using 20,000 sample data points from hotels_train 

```{r}
set.seed(1818)
train_sample = sample_n(hotels_train, 20000)
```

```{r}

enet_mod_all <- cva.glmnet(is_canceled ~ .,
                       data = train_sample,
                       family = "binomial",
                       alpha = seq(0,1, by = 0.05))

```

Min Loss Plot

```{r}
minlossplot(enet_mod_all,
cv.type = "min")
```

```{r}
#to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(mod) {min(mod$cvm)})
  alpha[which.min(error)]
}

# Get all parameters.
get_model_params <- function(fit) {
  alpha <- fit$alpha
  lambdaMin <- sapply(fit$modlist, `[[`, "lambda.min")
  lambdaSE <- sapply(fit$modlist, `[[`, "lambda.1se")
  error <- sapply(fit$modlist, function(mod) {min(mod$cvm)})
  best <- which.min(error)
  data.frame(alpha = alpha[best], lambdaMin = lambdaMin[best],
             lambdaSE = lambdaSE[best], eror = error[best])
}

# BEST MODEL 
# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod_all)
get_model_params(enet_mod_all)

# extract the best model object
best_mod <- enet_mod_all$modlist[[which(enet_mod_all$alpha == best_alpha)]]
```

2. Created another model using best alpha & full training set
```{r}

enet_mod2 <- cv.glmnet(is_canceled ~ .,
                       data = hotels_train,
                       family = "binomial",
                       alpha = 1)

```

Binomial Deviance Plot
```{r}
plot(enet_mod2)
print(enet_mod2$lambda.min)
# 
print(enet_mod2$lambda.1se)
```

Elastic Net Coefficients
```{r}
enet_coefs2 <- data.frame(
  `lasso_min` = coef(enet_mod2, s = enet_mod2$lambda.min) %>%
    as.matrix() %>% data.frame() %>% round(3),
  `lasso_1se` = coef(enet_mod2 , s = enet_mod2$lambda.1se) %>% 
    as.matrix() %>% data.frame() %>% round(3)
) %>%  rename(`enet_min` = 1, `enet_1se` = 2)  %>% 
print(enet_coefs2)
```

Coefficient Plot
```{r}
library ("coefplot")
coefpath(enet_mod2)
```


Scores for Train & Test
```{r}
library('yardstick')

scores_train_tree <- predict(enet_mod2, 
                             newdata = hotels_train,
                             type = "response")


scores_test_tree <- predict(enet_mod2, 
                            newdata = hotels_test,
                            type = "response")

head(scores_train_tree)
head(scores_test_tree)
```

Results for Train & Test

```{r}
library('yardstick')

results_train2 <- data.frame(

  `truth` = hotels_train   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.factor(is_canceled)),
   `Class1` =  scores_train_tree,
   `type` = rep("train",length(scores_train_tree)),
   `predicted` = as.factor(ifelse(scores_train_tree> 0.4,1,0)))


results_test2 <- data.frame(
  `truth` = hotels_test   %>% 
       filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.factor(is_canceled)),
   `Class1` =  scores_test_tree,
   `type` = rep("test",length(scores_test_tree)),
   `predicted` = as.factor(ifelse(scores_test_tree> 0.4,1,0))) 


head(results_train2)
head(results_test2)

```

Confusion Matrix for Train & Test
```{r}

cm_train <- conf_mat(results_train2, 
                      truth = is_canceled,
                      estimate = predicted)
print(cm_train)              

cm_test <- conf_mat(results_test2, 
                truth = is_canceled,
                estimate = predicted)
print(cm_test) 

```

Accuracy, Specificity, & Sensitivity for Train & Test
```{r}

summary(cm_train)
summary(cm_test)

```

```{r}
library('yardstick')

results_train3 <- data.frame(

  `truth` = hotels_train   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(is_canceled)),
   `Class1` =  scores_train_tree,
   `type` = rep("train",length(scores_train_tree)),
   `predicted` = as.numeric(ifelse(scores_train_tree> 0.4,1,0)))


results_test3 <- data.frame(
  `truth` = hotels_test   %>% 
       filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
             !is.na(arrival_date_year),
             !is.na(arrival_date_week_number),
             !is.na(arrival_date_day_of_month),
             !is.na(stays_in_week_nights),
             !is.na(stays_in_weekend_nights),
             !is.na(adults),
             !is.na(children),
             !is.na(babies),
             !is.na(meal),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
             !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
             !is.na(deposit_type),
             !is.na(days_in_waiting_list),
             !is.na(customer_type),
             !is.na(total_of_special_requests),
             !is.na(required_car_parking_spaces),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(is_canceled)),
   `Class1` =  scores_test_tree,
   `type` = rep("test",length(scores_test_tree)),
   `predicted` = as.numeric(ifelse(scores_test_tree> 0.4,1,0))) 


head(results_train3)
head(results_test3)

```

R2 
```{r}
rsq(results_train3, is_canceled, predicted)
rsq(results_test3, is_canceled, predicted)
```

1. Elastic Net testing different alphas using entire hotels_train (after presentation)
```{r}

enet_mod_all2 <- cva.glmnet(is_canceled ~ .,
                       data = hotels_train,
                       family = "binomial",
                       alpha = seq(0,1, by = 0.05))

```


```{r}
minlossplot(enet_mod_all2,
cv.type = "min")
```

```{r}
#to find the best alpha
get_alpha <- function(fit) {
  alpha <- fit$alpha
  error <- sapply(fit$modlist, 
                  function(mod) {min(mod$cvm)})
  alpha[which.min(error)]
}

# Get all parameters.
get_model_params <- function(fit) {
  alpha <- fit$alpha
  lambdaMin <- sapply(fit$modlist, `[[`, "lambda.min")
  lambdaSE <- sapply(fit$modlist, `[[`, "lambda.1se")
  error <- sapply(fit$modlist, function(mod) {min(mod$cvm)})
  best <- which.min(error)
  data.frame(alpha = alpha[best], lambdaMin = lambdaMin[best],
             lambdaSE = lambdaSE[best], eror = error[best])
}

# BEST MODEL 
# extract the best alpha value and model parameters
best_alpha <- get_alpha(enet_mod_all)
get_model_params(enet_mod_all)

# extract the best model object
best_mod <- enet_mod_all$modlist[[which(enet_mod_all$alpha == best_alpha)]]
```

Modified dataset based on lasso coefficient importance
```{r}
hotels_train_clean2 <- hotels_train %>% mutate(market_segment = fct_other(market_segment, drop= c("Aviation", "Groups", "Undefined")),
                                              reserved_room_type =fct_other(reserved_room_type, drop= c( "D", "H", "L")),
distribution_channel=fct_other(distribution_channel, drop=c( "TA/TO", "Undefined")),
assigned_room_type = fct_other(assigned_room_type, drop=c("C,", "D", "H")))

hotels_test_clean2 <- hotels_test %>% mutate(market_segment = fct_other(market_segment, drop= c("Aviation", "Groups", "Undefined")),
                                              reserved_room_type =fct_other(reserved_room_type, drop= c( "D", "H", "L")),
distribution_channel=fct_other(distribution_channel, drop=c( "TA/TO", "Undefined")),
assigned_room_type = fct_other(assigned_room_type, drop=c("C,", "D", "H")))

```

## 4.Predict Cancellations using Decision Tree

Prune the tree
```{r}
library(rpart)
hotel_mod_rpart <- rpart(is_canceled ~ ., 
                           data = hotels_train_clean2,
                           method = "class",
                           control = list(cp = 0, 
                                          minsplit = 5,
                                          maxdepth = 8))
plotcp(hotel_mod_rpart)

```

Create decision tree with maximum depth of 12
```{r }
library('partykit') 

hotel_tree_12<- ctree(is_canceled ~ ., 
                    
                      data = hotels_train_clean2,
                    
                     maxdepth = 12,
                    )

plot(hotel_tree_12, gp = gpar(fontsize = 6))

```

Create Predictions
```{r}
library('yardstick')

scores_train_tree <- predict(hotel_tree_12, 
                       type = "response")


scores_test_tree <- predict(hotel_tree_12, 
                       newdata = hotels_test_clean2,
                       type = "response")

head(scores_train_tree)
head(scores_test_tree)
```

Make Results Tables
```{r}

results_train_tree <- data.frame(
  `truth` = hotels_train_clean2   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
           !is.na(arrival_date_year),
           !is.na(arrival_date_week_number),
           !is.na(arrival_date_day_of_month),
           !is.na(stays_in_weekend_nights),
           !is.na(stays_in_week_nights),
             !is.na(adults),
           !is.na(children),
           !is.na(babies),
             !is.na(meal),
             !is.na(market_segment),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
           !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
              !is.na(deposit_type),
           !is.na(days_in_waiting_list),
             !is.na(customer_type),
           !is.na(required_car_parking_spaces),
             !is.na(total_of_special_requests),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(ifelse(is_canceled == 0,"0","1"))),
   `type` = rep("train",length(scores_train_tree)),
   `predicted` = as.numeric(ifelse(scores_train_tree == 0,"0","1")))


results_test_tree <- data.frame(
  `truth` = hotels_test_clean2   %>% 
       filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
           !is.na(arrival_date_year),
           !is.na(arrival_date_week_number),
           !is.na(arrival_date_day_of_month),
           !is.na(stays_in_weekend_nights),
           !is.na(stays_in_week_nights),
             !is.na(adults),
           !is.na(children),
           !is.na(babies),
             !is.na(meal),
             !is.na(market_segment),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
           !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
              !is.na(deposit_type),
           !is.na(days_in_waiting_list),
             !is.na(customer_type),
           !is.na(required_car_parking_spaces),
             !is.na(total_of_special_requests),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.numeric(ifelse(is_canceled == 0,"0","1"))),
   `type` = rep("test",length(scores_test_tree)),
   `predicted` = as.numeric(ifelse(scores_test_tree == 0,"0","1"))) 


head(results_train_tree)
head(results_test_tree)
```

Decision tree RMSE and RSQ 
```{r}
library('yardstick')
rmse(results_train_tree, is_canceled, predicted)
rmse(results_test_tree, is_canceled, predicted)
rsq(results_train_tree, is_canceled, predicted)
rsq(results_test_tree, is_canceled, predicted)
```

Confusion Matrix
```{r}
results_test_tree_factor <- data.frame(
  `truth` = hotels_test_clean2   %>%  
    filter(!is.na(is_canceled),
             !is.na(hotel),
             !is.na(lead_time),
             !is.na(arrival_date_month),
           !is.na(arrival_date_year),
           !is.na(arrival_date_week_number),
           !is.na(arrival_date_day_of_month),
           !is.na(stays_in_weekend_nights),
           !is.na(stays_in_week_nights),
             !is.na(adults),
           !is.na(children),
           !is.na(babies),
             !is.na(meal),
             !is.na(market_segment),
             !is.na(distribution_channel),
             !is.na(is_repeated_guest),
             !is.na(previous_cancellations),
           !is.na(previous_bookings_not_canceled),
             !is.na(reserved_room_type),
             !is.na(assigned_room_type),
             !is.na(booking_changes),
              !is.na(deposit_type),
           !is.na(days_in_waiting_list),
             !is.na(customer_type),
           !is.na(required_car_parking_spaces),
             !is.na(total_of_special_requests),
             !is.na(adr))  %>% 
    select(is_canceled) %>% 
    mutate(is_canceled = as.factor(ifelse(is_canceled == 0,"0","1"))),
   `type` = rep("train",length(scores_test_tree)),
   `predicted` = as.factor(ifelse(scores_test_tree == 0,"0","1")))


confusion_matrix  <- conf_mat(results_test_tree_factor, 
               truth = is_canceled,
               estimate = predicted)
print(confusion_matrix)

```

Get accuracy through summary
```{r}
summary(confusion_matrix)
```

Create and plot decision tree with maximum depth of 4
```{r}
library(partykit) 

hotel_tree_4 <- ctree(is_canceled ~ ., 
                    
                      data = hotels_train_clean2,
                    
                     maxdepth = 4,
                    )

plot(hotel_tree_4, gp = gpar(fontsize = 6))

```